Web Service Community \\ Learning

### 2014-06-12 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\IEEEPARstart{O}{ver} the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue. These services can be utilized on top of intelligent decision making agents in order to maximize gain by finding ways of providing services better satisfying end users. The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interaction, composition, and cooperation are the key challenges [references]. To this end the idea of \emph{community} of web services by gathering services having similar functionality but distinct non-functional properties was developed [references].

Web service communities facilitate the discovery of web services and also provide services with better quality. These communities act as abstract web services, communicating with external entities via same standard protocols the normal web services employ. Users send their requests to the coordinators of those communities, which play the role of their representatives or access points. The community coordinator in this \emph{community centralized} architecture is responsible for community management tasks such as verification of credentials of new web services before accepting them to join the community and also firing web services which do not add enough value to the community. Within communities,

@@

*******THIS ONE IS TEMPRORARY FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******THIS ONE IS TEMPRORARY FROM PREVIOUS WORKS*******

>>>>

\IEEEPARstart{O}{ver} the past years, online services have become important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One approach to deliver high quality service is utilizing intelligent decision making agents that are aimed at maximizing gain by exploring best ways of providing services that satisfy end users. The recent developments attempted to shift web services from passive model in the form of individual components to autonomous and group-based components that follow common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that have direct influence on group's overall performance in achieving common goals. All that being said, the idea of \emph{community} of web services has been emerged that gathers services having similar functionality but distinct non-functional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web service runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

The advantages of community of Web service is that they facilitate the discovery of web services and as community, they provide better quality services. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The community coordinator in \emph{community centralized} architecture is responsible for task recieve/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.

@@

*******THIS ONE IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******THIS ONE IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
